Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
.
pass on results

In this study, we analyzed the impact of two orthogonal dimensions in
bug finding: test mining and fuzzing. The first dimension focuses on
the impact of new inputs in bug finding whereas the second dimension
focuses on the impact of variations of existing inputs in bug finding.

\subsection{Test Mining}

In this experiment, we ran all tests (see Section~\ref{sec:seeds})
using our infrastructure in no-fuzzing mode. We inspected all warnings
reported by our tool and, for those we found suspicious, we filed a
bug report in the corresponding bug tracker.

@@

The rationale for considering fuzzing as a dimension of study is to
assess the extent to which changing existing inputs helps in finding
new bugs. We measured this ability both in absolute terms and
relatively to the number of bugs found with the seed inputs in
no-fuzzing mode.

>>>>

The overarching goal of our study is to identify the ability of simple
techniques to find bugs in \js\ engines with cross-engine differential
testing.  We analyzed the impact of two orthogonal dimensions in this
study: test mining and fuzzing. The first dimension focuses on the
impact of inputs, mined from the web, in bug finding whereas the
second dimension focuses on the impact of fuzzing these inputs.

In the following, we describe the methodology we used in this
experiment. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report in
the bug tracker including the test input that manifested the potential
problem and explaining the reasons we were suspicious. In some cases,
we used the Mozila lithium tool~\cite{lithium} to minimize the test
case. For the cases of false positives, we classified the reason for
the misclassification and moved to the next
bucket. Table~\ref{tab:summary-of-results} summarizes our results. It
shows, for each execution mode and category of bucket (\ie{}, hi or
lo), the total number of files involved, the number of buckets
reported, and the percentage of those that resulted in a bug
report. \Fix{elaborate summary} We elaborate those results in the
following.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{2}{c}{buckets} \\
    \cline{4-5}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\% positive} \\
    \midrule
    \multirow{2}{*}{no-fuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

\subsection{No Fuzzing}

This section reports the results obtained without fuzzing. The goal is
to observe the impact of the mined test cases in revealing
differential bugs. In this experiment, we ran all tests (see
Section~\ref{sec:seeds}) using our infrastructure in no-fuzzing
mode.

@@

This section reports the results obtained by fuzzing inputs with
existing tools. It is important to mention that, to avoid experimental
noise, we did not consider the \Fix{XX} files (\Fix{2.8\%} of the
total) reported in the previous experiment, \ie{}, we only fuzzed test
files whose output is consistent across all engines analyzed.
